IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/retrofit.tex
nit
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Different from more traditional fine-grained language-based IFC systems that
associate labels with values~\cite{sabelfeld2003language,
Austin:Flanagan:PLAS09}, we follow~\cite{Zeldovich:2006, lio} in taking a
coarse-grained floating-label approach and associating labels with
\emph{tasks}.
%
The task label---we refer to the label of the currently executing task as the
\emph{current label}---serves to protect everything in the task's scope;
all data in a task shares this common label.
%
Hence before performing a reads or a write, the IFC monitor inspects the
current label to decide whether the operation is permitted.
%
A task can only write to entities that are at least as sensitive.
%
Similarly, it can only read from entities that are less sensitive.
%
However, as in other floating-label systems, this current label can be raised
to allow the task to read from more sensitive entities at the cost of giving up
the ability to write to certain entities.

>>>>

As opposed to more traditional fine-grained language-based IFC systems that
associate labels with values~\cite{sabelfeld2003language,
Austin:Flanagan:PLAS09}, we follow~\cite{Zeldovich:2006, lio} in taking a
coarse-grained floating-label approach and associating labels with
\emph{tasks}.
%
The task label---we refer to the label of the currently executing task as the
\emph{current label}---serves to protect everything in the task's scope;
all data in a task shares this common label.
%
Hence before performing a reads or a write, the IFC monitor inspects the
current label to decide whether the operation is permitted.
%
A task can only write to entities that are at least as sensitive.
%
Similarly, it can only read from entities that are less sensitive.
%
However, as in other floating-label systems, this current label can be raised
to allow the task to read from more sensitive entities at the cost of giving up
the ability to write to certain entities.
